# Reproducible research in the study of biological coloration

[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.16949.svg)](http://dx.doi.org/10.5281/zenodo.16949)

This paper is now in press, and can be cited as:

[White TE, Dalrymple RL, Noble DWA, O’Hanlon JC, Zurek DB, Umbers KDL (2015) Reproducible research in the study of biological colouration. *Animal Behaviour*, in press](http://dx.doi.org/10.1016/j.anbehav.2015.05.007)

### Introduction
This repository contains data collected from the literature to assess to quality of reporting in signal-based colour studies of animal and plant taxa. Our literature search includes studies collected in 2013 from research journals likley to do colour signal research. We also detail important methodological details that ideally should be reported in studies that quantify colour using both spectrophotometry and camera equipment along with important analytical parameters used for visual modelling. 

### Executing code and compiling the manuscript

To compile the manuscript use 'knitr' to knit the ms.Rmd file to a markdown, ms.md file. This can all be done in the R console. First you need to set your working directory to this respository and then you can create the markdown file by sourcing the knit_doc.R file in the R folder as follows:

```{r, eval = FALSE, echo = TRUE}
# Set wd to col_sci repo
setwd("[INSERT PATH]/colsci_rep/")

# Source the knit_doc.R
source("R/knit_doc.R")
```

This command will generate a markdown file (ms.md) which can then be used to compile the manuscript in .pdf or .dox using pandoc. In terminal navigate to the 'docs/' folder in the colsci_rep repository and run:

```{r, eval = FALSE, echo = TRUE}
pandoc ms.md -o ms.pdf --bibliography references.bib --csl ref_style.csl -H ms.sty
```

Note that you will need pandoc and LaTex installed on your computer (http://pandoc.org).

If you have any troubles please don't hesitate to contact the authors: Daniel Noble and Tom White for more information.